Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support).

### 2017-02-10 csf-2017/paper.tex
added copy of f1 lemma

\newtheorem{theorem}{Theorem}

@@

>>>>

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}

@@

\begin{lemma}[Correctness lemma for \texttt{f1}]
  \label{lem:correctness-f1}
  Let
  \begin{align*}
    c_{\var{adv}} & \defeq ((\entry,\glob),\start_{\adv},\addrend_{\adv},\start_{\adv}+\olf) \\
    c_{f1} & \defeq ((\rwx,\glob),\mathtt{f1}-\olf,\mathtt{1f},\mathtt{f1}) \\
    c_\malloc & \defeq ((\entry,\glob),\start_\malloc,\addrend_\malloc,\start_\malloc+\olf) \\
    c_{\var{stk}} & \defeq ((\rwlx,\local),\start_\stk,\addrend_\stk,\start_\stk-1) \\
    c_\link & \defeq ((\readonly,\glob),\link,\link+1,\link)\\
    \reg & \in \Regs \\
    m & \defeq \hs_{f1} \uplus 
        \hs_\flag \uplus                
        \ms_{\var{link}} \uplus 
        \hs_\adv \uplus 
        \ms_{\malloc} \uplus 
        \ms_{\var{stk}} \uplus
        \ms_{\var{frame}} 
  \end{align*}
  and
  \begin{itemize}
  \item $c_\malloc$ satisfies the specification for malloc and $\iota_{\malloc,0}$ is the region from the specification.
  \end{itemize}
  where 
  \begin{align*}
    &\dom(\hs_{f1}) = [\mathtt{f1}-\olf,\mathtt{1f}] \\
    &\dom(\hs_\flag) = [\flag,\flag] \\
    &\dom(\ms_\link) = [\link,\link+1]\\
    &\dom(\ms_\stk) = [\start_\stk, \addrend_\stk]\\
    &\dom(\hs_{\adv}) = [\start_\adv,\addrend_\adv] \\
    &\heapSat[\hs_{\malloc}]{n}{[0 \mapsto \iota_{\malloc,0}]} \qquad \text{ for all $n \in \nats$}
  \end{align*}
  and
  \begin{itemize}
  \item $\ms_{f1}(\mathtt{f1}-\olf) = ((\readonly,\glob),\link,\link+1,\link)$, $\ms_{f1}(\mathtt{f1}-\olf+1) = ((\readwrite,\glob),\flag,\flag,\flag)$, the rest of $\hs_{f1}$ contains the code of $f1$.
  \item $\ms_\flag = [\flag \mapsto 0]$
  \item $\ms_{\var{link}} = [\var{link} \mapsto c_\malloc, \var{link} + 1 \mapsto c_\adv]$
  \item $\hs_\adv(\start_\adv) = c_\link$ and $\forall \addr \in [\start_\adv+1,\addrend]\ldotp \ms_\adv(a) \in \ints$
  \end{itemize}
  if 
  \[
    (\reg\update{\pcreg}{c_{f1}}\update{r_\stk}{c_\stk},m) \step[n] (\halted,m'),
  \]
  then
  \[
    m'(\flag) = 0
  \]  
\end{lemma}
